Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-09-23 manuscript/manuscript.tex
re-render

There are numerous possible uses for the chlorophyll \emph{a} and
microcystin-LR advisory cut-off values. First, in the absence of
microcystin-LR measurements, exceedence of the chlorophyll \emph{a}
concentrations could be a trigger for further actions. Given that there
is uncertainity around these chlorophyll \emph{a} cutoffs the best case
scenario would be to monitor for chlorophyll and in the event of
exceeding a target concentration take water samples and have those
samples tested in a lab for microcystin-LR. A second potential use is to
identify possible bloom events from historical data. Currently, there
are several suggestions on how to identify a bloom event, but there is
variation across the definitions and quantitative links to measures of
cyanobacteria are not always included {[}REFS{]}. Using our chlorophyll
\emph{a} cutoffs provides a value that is directly associated with
microcystin-LR and can be used to classify lakes, from past surveys, as
havin bloomed.

@@

>>>>

There are numerous possible uses for the chlorophyll \emph{a} and
microcystin-LR advisory cut-off values. First, in the absence of
microcystin-LR measurements, exceedence of the chlorophyll \emph{a}
concentrations could be a trigger for further actions. Given that there
is uncertainity around these chlorophyll \emph{a} cutoffs the best case
scenario would be to monitor for chlorophyll and in the event of
exceeding a target concentration take water samples and have those
samples tested in a lab for microcystin-LR. A second potential use is to
identify possible bloom events from historical data. As harmful algal
blooms are made up of many species and have various mechanism
responsible for adverse impacts (e.g.~toxins, hypoxia, odors), there is
no single definition of a bloom. For cHABs one approach has been to
identify an increase over a baseline concentration of phycocyanin
(Miller et al. 2013). This is a useful approach for targeted studies,
but phycocyanin is also not always available and measures the
predominance of cyanobacterial pigments and not toxins. Using our
chlorophyll \emph{a} cutoffs provides a value that is more directly
associated with microcystin-LR and can be used to classify lakes, from
past surveys, as having bloomed.

@@

Miller, T. R., L. Beversdorf, S. D. Chaston, and K. D. McMahon. 2013.
Spatiotemporal molecular analysis of cyanobacteria blooms reveals
microcystis-aphanizomenon interactions. PloS one 8:e74933.
